Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment

### 2018-05-31 Chapter-3/3-TheLArIATExperiment.tex
s

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The instrumentation of  LArIAT tertiary beam and the TPC components have changed several times during the three years of LArIAT data taking. The following paragraphs describe the components operational during ``Run II", the data taking period relevant to the hadron cross section measurements considered in this thesis.

@@

The current through the magnets at a given time is identical in both magnets. For the Run II data taking period, the current settings explored were 60A (B $\sim$0.21 T) and 100A (B $\sim$0.35 T) in both polarities. 
Albeit advantageous to enrich the tertiary beam composition with high mass particles such as kaons, we never pushed the magnets current over 100 A, not to incur in overheating.  During operation, we operated an air and water cooling system on the magnets and we remotely monitored the magnet temperatures.

@@

The punch-through is simple sheet of scintillator material, read out by two PMTs. 
The MuRS is a segmented block of steel with four slots instrumented with scintillation bars. The four steel layers in front of each instrumented slot are 2 cm, 2 cm, 14 cm and 16 cm deep in the beam direction. Each instrumented slot is equipped with four scintillation bars each, positioned horizontally in the direction orthogonal to the beam. Each scintillator bar measures  \textcolor{red}{? x ? x 2}~cm and it is read out by one PMT.

@@

It is worth mentioning here the presence of an additional scintillation paddle between WC4 and the downstream paddle of the TOF system, called halo. The halo is a 39x38x1 cm$^3$ paddle with a 6.5 cm radius hole in the center, whose original function was to reject  beam particles slightly offset from the beamline center. Data from this paddle turned out to be unusable, so our data events include both particle going through the halo scintillation material or through the halo hole.

@@

%%%%%%%%%%%%%%%%%%%%%
As in any other LArTPC, argon purity is a crucial parameter for LArIAT. Indeed, the presence of contaminants affects both the basic working principles of a LArTPC, as shown in section \ref{sec:LArTPCWorkingPrinciple}: electronegative contaminants such as oxygen and water decrease the number of ionization electrons collected on the wires after drifting through the volume. In addition, contaminants such as Nitrogen decrease the light yield from scintillation light, especially in its slow component.
In LArIAT, contaminations should not exceed the level of 0.2 parts per billion (ppb). We achieve this level of purity in several stages. The specifics required for the commercial argon bought for LArIAT are 2 parts per million (ppm) oxygen, 3.5~ppm water, and 10~ppm nitrogen. This argon is monitored with the use of commercial gas analyzer.
Argon is stored in a dewar external to LArIAT hall and filtered before filling the TPC. %The argon is delivered from the commercial dewar to the cryostat through 2.54~cm diameter schedule 10 stainless steel piping.  The piping was insulated with 20.32~cm of polyurethane foam by the manufacturer.  The piping was cleaned to remove oil and grease before being welded into the system. 
LArIAT uses a filtration system designed for the Liquid Argon Purity Demonstrator (LAPD)~\cite{LAPD}: half of a 77~liter filter contains a 4A molecular sieve (Sigma-Aldrich~\cite{sigma-aldrich}) able to remove mainly water, while the other half contains BASF~CU-0226~S, a highly dispersed copper oxide impregnated on a high surface area alumina, apt to remove mainly oxygen~\cite{basf}. A single pass of argon in the filter is sufficient to achieve the necessary purity, unless the filter is saturated. In case the filter saturates, the media needs to be regenerated by using heated gas; this happened twice during the Run II period\footnote{We deemed the filter regeneration necessary every time the electron lifetime dropped under 100 \textmu s.}. The electron lifetime during the full LArIAT data taking are shown in Figure \ref{fig:Elifetime}.
The filtered argon reaches the inner vessel via a liquid feedthrough which is routed to the bottom of the cryostat. Argon is not recirculated in the system; rather, it boils off and vents to the atmosphere. During data taking, we replenish the argon in the cryostat every 6 hours to keep the TPC high voltage feedthrough and cold electronics always submerged. In fact, we constantly monitor the level, temperature, and pressure of the argon both in the commercial dewar and inside the cryostat during data taking. 
\subsection{LArTPC: Charge Collection}\label{sec:TPCCharge}
The LArIAT Liquid Argon Time Projection Chamber is a rectangular box of dimensions 47 cm (drift) x 40 cm (height) x 90 cm (length), containing 170 liters of Liquid Argon.
The LArTPC three major subcomponents are 
\begin{itemize} 
\item[1)] the cathode and field cage,
\item [2)] the wire planes, 
\item [3)] the read-out electronics. %
\end{itemize}

@@

Dedicated electronics read the induction and collection plane wires, for a total of  480-channel analog signal path from the TPC wires to the signal digitizers. A digital control system for the TPC-mounted electronics, a power supply, and a distribution system complete the front-end system. Figure \ref{pic:FEelectronics} shows a block diagram of the overall system. The direct readout of the ionization electrons in liquid argon forms typically small signals on the wires, which need amplification in oder to be processed. LArIAT  performs the amplification stage directly in cold with  amplifiers %developed by the Brookhaven National Lab (BNL) and 
mounted on the TPC frame inside the liquid argon. The BNL ASICs adopted in LAriAT are designated as LArASIC, version 4-star and are the same used by the MicroBooNE experiment \cite{Acciarri2017}.
%The ASIC signals for each wire are then driven out of the vessel  to DAQ boards that act as waveform recorders.
The signal from the ASICs are driven to the other end of the readout chain, to the CAEN V1740 digitizers \cite{CAENV1740}. The CAEN V1740 has a 12 bit resolution and a maximum input range of 2~VDC, resulting in about 180 ADC count for a crossing MIP.

@@

Fundamental inputs to the trigger card come from the TOF (see section~\ref{sec:TOF}) and the wire chambers (see section~\ref{sec:MWPC}), as activity in these systems points to the presence of a charged particle in tertiary beam line.
In particular, the discriminated pulses from the TOF PMTs form a NIM logic pulse for the trigger logic. We ask for a coincidence within a 20~ns window for all the pulses from the PMTs looking at the same scintillator block and use a delayed coincidence between the upstream and downstream paddle to inform the trigger decision. In order to form a coincidence between the upstream and downstream paddles, we delay the upstream paddle coincidence by 20~ns and widen it by 100~ns. The delay and widening are necessary to account for both  lightspeed particles and slower particles (high-mass) to travel the 6.5~m between the upstream and the downstream paddles. 
For the read out of the wire chambers, we use a total of sixteen multi-hit TDCs\cite{Sten}, four per chamber: two TDC per plane (horizontal and vertical), sixty-four wires per TDC. In each TDC, we keep the logical ``OR" for any signal over threshold from the sixty-four wires. We then require a coincidence between the ``OR" for the horizontal TDCs and the ``OR" for the vertical TDCs: with this logic we make sure that at least one horizontal wire and one vertical wire saw significant signal in one wire chamber.  The single logical pulse from each of the four wire chambers feeds into the first four inputs to the V1495 trigger card. We require a coincidence within 20~ns of at least three logical inputs to form a trigger.

@@

\section{Control Systems}
LArIAT is a complex ensemble of systems which needed to be monitored simultaneously during data taking.  We performed the monitoring of the systems operations with a slow control system, a DAQ monitoring system and a low level data quality monitoring described in the following sections.

\subsubsection{Slow Control}
We used the Synoptic Java Web Start framework \cite{Synoptic} as a real-time display of subsystem conditions. Synoptic provides a Graphical User Interface that talks to the Fermilab Accelerator Control System via the ACNET protocol. Its simple GUI allowed us to change the operating parameters and to graph the trends of several variables of interest for all of the tertiary beam detectors.  Among the most important quantities monitored by Synoptic there are the level of argon in both the inner vessel and the external dewar, the operating voltages of cathode and wire planes, of the PMTs and SiPMs, and of the four wire chambers, as well as the magnet temperatures. Figure \ref{fig:synoptics} shows an example of the monitoring system.
LArIAT uses the Accelerator Control NETwork system (ACNET) to monitor the beam conditions of the MCenter beamline. For example, the horizontal and vertical position of the beam at the first two wire chambers (WC1 and WC2) are shown in \ref{fig:ACNET} as seen by the shifter during data taking.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The instrumentation of the LArIAT tertiary beam and the TPC components have changed several times during the three years of LArIAT data taking. The following paragraphs describe the components operational during ``Run II", the data taking period relevant to the hadron cross section measurements considered in this thesis.

@@

The current through the magnets at a given time is identical in both magnets. For the Run II data taking period, the current settings explored were 60A (B $\sim$0.21 T) and 100A (B $\sim$0.35 T) in both polarities. 
Albeit advantageous to enrich the tertiary beam composition with high mass particles such as kaons, we never pushed the magnets current over 100 A, so as not to incur in overheating.  During operation, we operated an air and water cooling system on the magnets and we remotely monitored the magnet temperatures.

@@

The punch-through is simple sheet of scintillator material, read out by two PMTs. 
The MuRS is a segmented block of steel with four slots instrumented with scintillation bars. The four steel layers in front of each instrumented slot are 2 cm, 2 cm, 14 cm and 16 cm deep in the beam direction. Each instrumented slot is equipped with four scintillation bars each, positioned horizontally in the direction orthogonal to the beam. Each scintillator is read out by one PMT.

@@

It is worth mentioning here the presence of an additional scintillation paddle between WC4 and the downstream paddle of the TOF system, called halo. The halo is a 39 x 38 x 1 cm$^3$ paddle with a 6.5 cm radius hole in the center, whose original function was to reject  beam particles slightly offset from the beamline center. Data from this paddle turned out to be unusable, so our data events include both particle going through the halo scintillation material or through the halo hole.

@@

%%%%%%%%%%%%%%%%%%%%%
As in any other LArTPC, argon purity is a crucial parameter for LArIAT. Indeed, the presence of contaminants affects both the basic working principles of a LArTPC, as shown in Section \ref{sec:LArTPCWorkingPrinciple}: electronegative contaminants such as oxygen and water decrease the number of ionization electrons collected on the wires after drifting through the volume. In addition, contaminants such as Nitrogen decrease the light yield from scintillation light, especially in its slow component.
In LArIAT, contaminations should not exceed the level of 0.2 parts per billion (ppb). We achieve this level of purity in several stages. The specifics required for the commercial argon bought for LArIAT are 2 parts per million (ppm) oxygen, 3.5~ppm water, and 10~ppm nitrogen. This argon is monitored with the use of commercial gas analyzer.
Argon is stored in a dewar external to LArIAT hall and filtered before filling the TPC. %The argon is delivered from the commercial dewar to the cryostat through 2.54~cm diameter schedule 10 stainless steel piping.  The piping was insulated with 20.32~cm of polyurethane foam by the manufacturer.  The piping was cleaned to remove oil and grease before being welded into the system. 
LArIAT uses a filtration system designed for the Liquid Argon Purity Demonstrator (LAPD)~\cite{LAPD}: half of a 77~liter filter contains a 4A molecular sieve (Sigma-Aldrich~\cite{sigma-aldrich}) able to remove mainly water, while the other half contains BASF~CU-0226~S, a highly dispersed copper oxide impregnated on a high surface area alumina, apt to remove mainly oxygen~\cite{basf}. A single pass of argon in the filter is sufficient to achieve the necessary purity, unless the filter is saturated. In case the filter saturates, the media needs to be regenerated by using heated gas; this happened twice during the Run II period\footnote{We deemed the filter regeneration necessary every time the electron lifetime dropped under 100 \textmu s.}. The electron lifetime during the full LArIAT data taking are shown in Figure \ref{fig:Elifetime}.
The filtered argon reaches the inner vessel via a liquid feedthrough which is routed to the bottom of the cryostat. Argon is not recirculated in the system; rather, it boils off and vents to the atmosphere. During data taking, we replenish the argon in the cryostat every 6 hours to keep the TPC high voltage feedthrough and cold electronics always submerged. In fact, we constantly monitor the level, temperature, and pressure of the argon both in the commercial dewar and inside the cryostat during data taking. 
\subsection{LArTPC: Charge Collection}\label{sec:TPCCharge}
The LArIAT Liquid Argon Time Projection Chamber is a rectangular box of dimensions 47 cm (drift) x 40 cm (height) x 90 cm (length), containing 170 liters of Liquid Argon.
The LArTPC three major subcomponents are 
\begin{itemize} 
\item[1)] the cathode and field cage,
\item [2)] the wire planes, 
\item [3)] the read-out electronics. %
\end{itemize}

@@

Dedicated electronics read the induction and collection plane wires, for a total of  480-channel analog signal path from the TPC wires to the signal digitizers. A digital control system for the TPC-mounted electronics, a power supply, and a distribution system complete the front-end system. Figure \ref{pic:FEelectronics} shows a block diagram of the overall system. The direct readout of the ionization electrons in liquid argon forms typically small signals on the wires, which need amplification in oder to be processed. LArIAT  performs the amplification stage directly in cold with  amplifiers %developed by the Brookhaven National Lab (BNL) and 
mounted on the TPC frame inside the liquid argon. The BNL ASICs adopted in LArIAT are designated as LArASIC, version 4-star and are the same used by the MicroBooNE experiment \cite{Acciarri2017}.
%The ASIC signals for each wire are then driven out of the vessel  to DAQ boards that act as waveform recorders.
The signal from the ASICs are driven to the other end of the readout chain, to the CAEN V1740 digitizers \cite{CAENV1740}. The CAEN V1740 has a 12 bit resolution and a maximum input range of 2~VDC, resulting in about 180 ADC count for a crossing MIP.

@@

Fundamental inputs to the trigger card come from the TOF (see Section~\ref{sec:TOF}) and the wire chambers (see Section~\ref{sec:MWPC}), as activity in these systems points to the presence of a charged particle in tertiary beam line.
In particular, the discriminated pulses from the TOF PMTs form a NIM logic pulse for the trigger logic. We ask for a coincidence within a 20~ns window for all the pulses from the PMTs looking at the same scintillator block and use a delayed coincidence between the upstream and downstream paddle to inform the trigger decision. In order to form a coincidence between the upstream and downstream paddles, we delay the upstream paddle coincidence by 20~ns and widen it by 100~ns. The delay and widening are necessary to account for both  lightspeed particles and slower particles (high-mass) to travel the 6.5~m between the upstream and the downstream paddles. 
For the read out of the wire chambers, we use a total of sixteen multi-hit TDCs\cite{Sten}, four per chamber: two TDC per plane (horizontal and vertical), sixty-four wires per TDC. In each TDC, we keep the logical ``OR" for any signal over threshold from the sixty-four wires. We then require a coincidence between the ``OR" for the horizontal TDCs and the ``OR" for the vertical TDCs: with this logic we make sure that at least one horizontal wire and one vertical wire saw significant signal in one wire chamber.  The single logical pulse from each of the four wire chambers feeds into the first four inputs to the V1495 trigger card. We require a coincidence within 20~ns of at least three logical inputs to form a trigger.

@@

\section{Control Systems}
LArIAT is a complex ensemble of systems which needed to be monitored simultaneously during data taking.  We performed the monitoring of the systems operations with a slow control system, a DAQ monitoring system and a low level data quality monitoring system described in the following sections.

\subsubsection{Slow Control}
We used the Synoptic Java Web Start framework \cite{Synoptic} as a real-time display of subsystem conditions. Synoptic provides a Graphical User Interface that talks to the Fermilab Accelerator Control System via the ACNET protocol. Its simple GUI allowed us to change the operating parameters and to graph the trends of several variables of interest for all of the tertiary beam detectors.  Among the most important quantities monitored by Synoptic are the level of argon in both the inner vessel and the external dewar, the operating voltages of cathode and wire planes, of the PMTs and SiPMs, and of the four wire chambers, as well as the magnet temperatures. Figure \ref{fig:synoptics} shows an example of the monitoring system.
LArIAT uses the Accelerator Control NETwork system (ACNET) to monitor the beam conditions of the MCenter beamline. For example, the horizontal and vertical position of the beam at the first two wire chambers (WC1 and WC2) are shown in \ref{fig:ACNET} as seen by the shifter during data taking.

### 2018-05-31 Chapter-4/4-Methodology.tex
s

\subsection{TPC Selection: Halo Mitigation }\label{ch:pileUp}
The secondary beam impinging on LArIAT secondary target produces a plethora of particles which propagates downstream. The presence of upstream and downstream collimators greatly abates the number of particles tracing down the LArIAT tertiary beamline. However, it is possible that more than one particle sneaks into the LArTPC during its readout time: the TPC readout is triggered by the particle  firing the series of beamline detectors along our tertiary beamline, but particles from the beam halo might also be present in the TPC at the same time. We call ``pile up" the additional traces in the TPC. We adjusted the primary beam intensity between LArIAT Run I and Run II to reduce the presence of events with high pile up particles in the data sample. For the cross section analyses, we remove events with more than 4 tracks in the first 14 cm upstream portion of the TPC from the sample (line 5 in in Table \ref{tab:beamlineDataSelection}).

\subsection{TPC Selection: Shower Removal}\label{ch:electrons}
In the case of the ($\pi^-$,Ar) cross section, the resolution of  beamline mass spectrometer is not sufficient to select a beam of pure pions. In fact,  muons which are close in mass to the pions and relativistic electrons survive the selection on the beamline mass.  It is important to notice that the composition of the negative polarity beam is mostly pions, as will be discussed in section \ref{ch:beamlineComposition}.
Still, we devise a selection on the TPC information to mitigate the presence of electrons in the sample used for the pion cross section. The selection relies on the different topologies of a pion and an electron event when propagating in liquid argon: while the former will trace a track inside the TPC active volume, the latter will tend to ``shower", i.e. interact with the medium, producing bremsstrahlung photons which pair convert into several short tracks. In order to remove the shower topology, we create a region of interest (ROI) around the TPC track corresponding to the beamline particle. We look for short tracks contained in the ROI, as depicted in figure \ref{fig:showerFilt}:  if more then 5 tracks shorter than 10 cm are in the ROI, we reject the event. Line 7 in  Table \ref{tab:beamlineDataSelection} shows the number of events surviving this selection; that table also shows that this selection is applied after the wire chamber to TPC match (discussed in the next section). The WC2TPC match already lower the presence of electrons in the sample, which is further reduced by the shower filter.

@@

\section{Beamline and TPC Handshake: the Wire Chamber to TPC Match}\label{ch:WC2TPCMatchMethod}
For each event passing the selection on its beamline information, we need to identify the track inside the TPC corresponding to the particle which triggered the beamline detectors, a procedure we refer to as ``WC to TPC match" (WC2TPC for short). In general, the TPC tracking algorithm can reconstruct more than one track in the event, partially due to the fact that hadrons interact in the chamber and partially because of pile up particles during the triggered TPC readout time, as shown in figure~\ref{fig:kaonInteraction}.

@@

We attempt to uniquely match one wire chamber track (see Section \ref{sec:MWPCfunc}) to one and only one reconstructed TPC track. 
In order to determine if a match is present, we apply a geometrical selection on the relative position of the wire chamber and TPC tracks. 
We start by considering only TPC tracks whose first point is in the first 2 cm upstream portion of the TPC for the match.  We project the wire chamber track to the TPC front face where we define the coordinates of the projected point as  $x_{FF}$ and $y_{FF}$.  For each considered TPC track, we define $\Delta$X as the difference between the $x$ position of the most upstream point of the TPC track and $x_{FF}$.  $\Delta$Y is defined analogously. We define the radius difference, $\Delta$R, as $ \Delta \text{R} =  \sqrt{ \Delta \text{X}^2 +  \Delta \text{Y}^2}  $. We define  as $\alpha$ the angle between the incident WC track and the TPC track in the plane that contains them.  If  $\Delta \text{R} < 4 $~cm, $\alpha < 8^\circ $,  a match between WC-track and TPC track is found. We describe  how we determine the value for the radius and angular selection in Section \ref{ch:WC2TPCMatchOptimization}.
We discard events with multiple WC2TPC matches. We use only those TPC tracks that are matched to WC tracks in the cross section calculation. Line 6 in Table \ref{tab:beamlineDataSelection} shows the number of events where a unique WC2TPC match was found.

@@

As we will show in section \ref{ch:PionXSBkgSub}, the background subtraction for the interacting and incident histograms can be translated into corresponding relative pion content factors $C^{\pi MC}_{\text{Int}} (E_{i})$ and $C^{\pi MC}_{\text{Inc}} (E_{i})$ and the cross section re-written as follows

>>>>

\subsection{TPC Selection: Halo Mitigation }\label{ch:pileUp}
The secondary beam impinging on LArIAT secondary target produces a plethora of particles which propagates downstream. The presence of upstream and downstream collimators greatly abates the number of particles traveling down the LArIAT tertiary beamline. However, it is possible that more than one particle sneaks into the LArTPC during its readout time: the TPC readout is triggered by the particle  firing the series of beamline detectors along our tertiary beamline, but particles from the beam halo might also be present in the TPC at the same time. We call ``pile up" the additional traces in the TPC. We adjusted the primary beam intensity between LArIAT Run I and Run II to reduce the presence of events with high pile up particles in the data sample. For the cross section analyses, we remove events with more than 4 tracks in the first 14 cm upstream portion of the TPC from the sample (line 5 in in Table \ref{tab:beamlineDataSelection}).

\subsection{TPC Selection: Shower Removal}\label{ch:electrons}
In the case of the ($\pi^-$,Ar) cross section, the resolution of  beamline mass spectrometer is not sufficient to select a beam of pure pions. In fact,  muons which are close in mass to the pions and relativistic electrons survive the selection on the beamline mass.  It is important to notice that the composition of the negative polarity beam is mostly pions, as will be discussed in section \ref{ch:beamlineComposition}.
Still, we devise a selection on the TPC information to mitigate the presence of electrons in the sample used for the pion cross section. The selection relies on the different topologies of a pion and an electron event when propagating in liquid argon: while the former will trace a track inside the TPC active volume, the latter will tend to ``shower", i.e. interact with the medium, producing bremsstrahlung photons which pair convert into several short tracks. In order to remove the shower topology, we create a region of interest (ROI) around the TPC track corresponding to the beamline particle. We look for short tracks contained in the ROI, as depicted in Figure \ref{fig:showerFilt}:  if more then 5 tracks shorter than 10 cm are in the ROI, we reject the event. Line 7 in  Table \ref{tab:beamlineDataSelection} shows the number of events surviving this selection; that table also shows that this selection is applied after the wire chamber to TPC match (discussed in the next section). The WC2TPC match already lower the presence of electrons in the sample, which is further reduced by the shower filter.

@@

\section{Beamline and TPC Handshake: the Wire Chamber to TPC Match}\label{ch:WC2TPCMatchMethod}
For each event passing the selection on its beamline information, we need to identify the track inside the TPC corresponding to the particle which triggered the beamline detectors, a procedure we refer to as ``WC to TPC match" (WC2TPC for short). In general, the TPC tracking algorithm can reconstruct more than one track in the event, partially due to the fact that hadrons interact in the chamber and partially because of pile up particles during the triggered TPC readout time, as shown in Figure~\ref{fig:kaonInteraction}.

@@

We attempt to uniquely match one wire chamber track (see Section \ref{sec:MWPCfunc}) to one and only one reconstructed TPC track. 
In order to determine if a match is present, we apply a geometrical selection on the relative position of the wire chamber and TPC tracks. 
We start by considering only TPC tracks whose first point is in the first 2 cm upstream portion of the TPC for the match.  We project the wire chamber track to the TPC front face where we define the coordinates of the projected point as  $x_{FF}$ and $y_{FF}$.  For each considered TPC track, we define $\Delta$X as the difference between the $x$ position of the most upstream point of the TPC track and $x_{FF}$.  $\Delta$Y is defined analogously. We define the radius difference, $\Delta$R, as $ \Delta \text{R} =  \sqrt{ \Delta \text{X}^2 +  \Delta \text{Y}^2}  $. We define  as $\alpha$ the angle between the incident WC track and the TPC track in the plane that contains them.  If  $\Delta \text{R} < 4 $~cm, $\alpha < 8^\circ $,  a match between WC-track and TPC track is found. We describe  how we determine the value for the radius and angular selection in Appendix \ref{ch:AppendixTrack}.
We discard events with multiple WC2TPC matches. We use only those TPC tracks that are matched to WC tracks in the cross section calculation. Line 6 in Table \ref{tab:beamlineDataSelection} shows the number of events where a unique WC2TPC match was found.

@@

As we will show in Section \ref{ch:PionXSBkgSub}, the background subtraction for the interacting and incident histograms can be translated into corresponding relative pion content factors $C^{\pi MC}_{\text{Int}} (E_{i})$ and $C^{\pi MC}_{\text{Inc}} (E_{i})$ and the cross section re-written as follows
